Context-dependent consequences of including lagged effects in demographic models

### 2022-06-01 docs/paper.Rmd
update manuscript to test GH pages

---
title: "Context-dependent consequences of including lagged effects in demographic models"
shorttitle: "Lagged Effects IPMs"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
    bookdown::html_document2: 
      theme: 
        version: 4
        bootswatch: journal
      number_sections: no
      fig_caption: yes
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights

@@

```{r lambdas, results='asis'}
tar_read(lambda_table) %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "DLNM" = "Stochastic, parameter-resampled"
    )
  )) %>% 
  select(IPM = ipm, Habitat = habitat, "$\\lambda$" = lambda) %>% 
pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambda) Population growth rates for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)

@@

knitr::include_graphics(tar_read(fig_pop_states))

>>>>

---
title: "Context-dependent consequences of including lagged effects in demographic models"
shorttitle: "Lagged Effects IPMs"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Emilio M. Bruna:

      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false
institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2: 
      theme: 
        version: 4
        bootswatch: journal
      number_sections: no
      fig_caption: yes
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights

@@

```{r lambdas, results='asis'}
tar_read(lambda_table) %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "DLNM" = "Stochastic, parameter-resampled"
    )
  )) %>% 
  select(IPM = ipm, Habitat = habitat, "$\\lambda$" = lambda) %>% 
pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambdas) Population growth rates for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)

@@

knitr::include_graphics(here::here(tar_read(fig_pop_states)))
